%-------------------------
% Resume in LaTeX
% Based on: https://github.com/sb2nov/resume
% Adapted for: Arkar Min - AI Engineer / Backend & LLM/RAG Systems
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
% ATS-friendly font setup: Helvetica-like sans-serif, clean and highly legible.
\usepackage[scaled=0.95]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% Section formatting
% Section headings use ~14pt equivalent for a clear ATS-friendly hierarchy.
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
% Body/list text stays around 10--11pt using \small for readability and one-page density.
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\LARGE Arkar Min} \\ \vspace{2pt}
    \small AI Engineer $|$ Backend Engineer \\ \vspace{1pt}
    \small 09756192218 $|$ \href{mailto:arkar.dev.kei@gmail.com}{\underline{arkar.dev.kei@gmail.com}} $|$
    \href{https://github.com/arkarmin-gg}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/arkar-min-97410b308/}{\underline{LinkedIn}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
\small{AI Engineer and Backend Software Engineer with 3+ years of experience building scalable backend platforms, production REST APIs, distributed systems and LLM-powered systems. Experienced in RAG pipelines, embeddings, vector search and AI agents systems. Strong background in secure API design, database architecture, multi-tenant SaaS systems, payment platforms, and practical AI product development from architecture to production deployment.}

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI / LLM / RAG}{: RAG Pipelines, Chunking, Embeddings, Vector Search, pgvector, Qdrant, Semantic Search, Prompt Engineering, AI Agents, Tool Calling, LLM Workflow Orchestration, Reranking, Knowledge Retrieval} \\
     \textbf{LLM APIs \& Frameworks}{: OpenAI API, AWS Rekognition, Openrouter API, Mastra, LangChain, LangGraph Orchestration, Llamaindex} \\
     \textbf{Backend}{: Python, FastAPI, SQLAlchemy, Alembic, Pydantic, TypeScript, Node.js, NestJS, ExpressJS, TypeORM} \\
     \textbf{Data / Cloud / DevOps}{: PostgreSQL, MySQL, MongoDB, Redis, Docker, Git, GitHub Actions, AWS S3, AWS Rekognition, BullMQ, Socket.IO}
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Origin Business Solutions}{March 2025 -- Present}
      {Software Engineer (Backend, AI)}{On-site / Myanmar}
      \resumeItemListStart
        \resumeItem{Design and develop secure, scalable, multi-tenant backend services and REST APIs for production business systems, improving maintainability, reliability, and high performance.}
        \resumeItem{Researched, developed, and integrated data pipelines, RAG systems, LLM-powered features, and AI agents into customer software and ERP systems.}
        \resumeItem{Develop end-to-end RAG pipelines covering ingestion, preprocessing, chunking, embedding generation, vector indexing, retrieval, reranking, and response generation.}
        \resumeItem{Managed Linux-based servers and configured CI/CD pipelines for faster, safer, and more reliable deployments.}
        \resumeItem{Managed and developed AWS infrastructure and Linux-based servers and VPS, including setup, maintenance, deployment, monitoring, and security auditing.}
        \resumeItem{.}
      \resumeItemListEnd

    \resumeSubheading
      {AlphaX}{July 2024 -- March 2025}
      {Full-stack Developer}{On-site / Myanmar}
      \resumeItemListStart
        \resumeItem{Developed and led full-stack web applications, CMS dashboards, and e-commerce platforms with secure backend APIs and maintainable frontend integrations.}
        \resumeItem{Built high-performance backend services using TypeScript, Node.js, REST APIs, database modeling, and modular architecture practices.}
        \resumeItem{Applied microservices-oriented designs to improve scalability, maintainability, and separation of business domains while debugging production issues under fast-moving client requirements.}
        \resumeItem{Collaborated with product and UI/UX teams to deliver full-stack solutions from requirement analysis to production deployment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Biz24 AI E-commerce SaaS Platform} $|$ \emph{Python, FastAPI, LangChain, PostgreSQL, Qdrant, Redis, BullMQ, Socket.IO}}{}
          \resumeItemListStart
            \resumeItem{Built a production-ready multi-tenant AI customer support platform enabling each shop to run a customizable LLM-powered support agent with RAG, persistent memory, multilingual responses, and real-time chat.}
            \resumeItem{Designed shop-scoped retrieval using PDF/text ingestion, document chunking, OpenAI-compatible embeddings, Qdrant vector search, and hybrid product search with PostgreSQL full-text search and Reciprocal Rank Fusion.}
            \resumeItem{Integrated agent tools for product questions, order status, cart management, checkout assistance, cancellation workflows, support-ticket escalation, and multi-channel web, Telegram, and Facebook Messenger support.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{MKI AI Material \& Asset Management System} $|$ \emph{FastAPI, Python, OpenAI, AWS, AWS Rekognition, MySQL}}{}
          \resumeItemListStart
            \resumeItem{Developed an AI-powered image-based asset classification backend using FastAPI, GPT-4o-mini, AWS Rekognition Custom Labels, S3, MySQL, SQLAlchemy, Alembic, and Pydantic for a Japanese construction company.}
            \resumeItem{Implemented LLM image reasoning to generate structured Japanese descriptions for shape, material, texture, pattern, color, and use case, then matched results against internal PDF knowledge records.}
            \resumeItem{Built ML data pipelines for S3 image organization, presigned URLs, dataset cleanup, Rekognition model startup, custom label detection, and Ground Truth-compatible training metadata updates.}
          \resumeItemListEnd

\resumeProjectHeading
  {\textbf{CRM \& Sales Agentic System} $|$ \emph{NodeJS, NestJS, PostgreSQL, TypeORM, Python, LangChain, pgvector}}{}
  \resumeItemListStart
    \resumeItem{Built a modular CRM backend for managing leads, customers, quotations, contracts, sales pipelines, bulk uploads, activity logs, analytics reports, user access, and document services.}
    \resumeItem{Designed an AI-powered quotation description generation architecture using LLMs, LangChain, pgvector, and RAG to generate professional quotation item descriptions from historically approved CRM data.}
    \resumeItem{Implemented a Sales AI Agent system to support human sales teams with lead analysis, quotation assistance, follow-up suggestions, customer context retrieval, and sales workflow automation.}
  \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{OBS Payment Gateway Backend} $|$ \emph{NodeJS, NestJS, TypeScript, PostgreSQL, TypeORM}}{}
          \resumeItemListStart
            \resumeItem{Developed a production-grade payment gateway backend unifying KBZPay, AYA Pay, Wave Pay, MPU, MMQR, APlus Pay, Visa, Mastercard, and JCB through a single REST API.}
            \resumeItem{Implemented centralized checkout sessions, API-key authentication, JWT-based request signing, duplicate order prevention, merchant redirects, provider callbacks, and transaction inquiry workflows.}
            \resumeItem{Built transaction lifecycle management, MDR/service-fee calculations, RBAC/CASL permissions, OTP login, audit logs, webhook trails, provider request logs, and merchant dashboard analytics.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Fair Price Taxi - Ride Hailing System} $|$ \emph{NodeJS, NestJS, PostgreSQL, Redis, BullMQ, Socket.IO, Firebase, AWS S3}}{}
          \resumeItemListStart
            \resumeItem{Built a production-grade ride-hailing backend supporting passenger, driver, and admin workflows including authentication, ride booking, real-time dispatch, transactions, notifications, and analytics.}
            \resumeItem{Implemented real-time driver dispatch with Socket.IO, Redis, and BullMQ, including location tracking, auto-reject timeouts, ride status updates, push notifications, and driver eligibility checks.}
            \resumeItem{Designed dynamic pricing for car grades, distance-based fares, peak-hour rules, special-location fees, add-ons, penalties, multi-destination fees, and fare rounding.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{University Student \& Payment Backend System} $|$ \emph{NodeJS, NestJS, TypeScript, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Engineered centralized university systems for student registration, payment workflows, admissions, academic structures, online examinations, financial transactions, and bulk data processing.}
            \resumeItem{Built external student validation APIs, dynamic fee calculation, multi-gateway aggregation, asynchronous webhooks, JWT/RBAC security, 2FA, Turnstile, activity logging, and high-performance ExcelJS pipelines.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Greenwich}{2022 -- 2025}
      {Bachelor of Science in Computing}{}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
